An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-12-01 latex-spie/article.tex
conclusion is added
captions are updated

@@

% DISTANCE MATRICES
\begin{figure}[!htb]
        \centering

% RESULTS
\begin{figure}[!htb]
        \centering

        %%% BRIGHT PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_bright.eps}    
        \caption{Bright dataset results.}
        \label{subfig:pr_bright}
        \end{subfigure}
        ~ 
        %%% DIM PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dim.eps}    
        \caption{Dim dataset results.}
        \label{subfig:pr_dim}
        \end{subfigure}
        ~
        %%% DARK PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dark.eps}    
        \caption{Dark dataset results.}
        \label{subfig:pr_dark}
        \end{subfigure}
        ~ 
        %%% ALL PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_all.eps}    
        \caption{Comparison between datasets.}
        \label{subfig:pr_all}
        \end{subfigure}

        \hspace{-3mm}
        \caption{PR curves}
        \label{fig:pr_curves}
\end{figure}

%----------------------------------------------------------------------------------------------------
% CONCLUSION AND FUTURE WORK
%----------------------------------------------------------------------------------------------------

\section{CONCLUSION AND FUTURE WORK}

>>>>

% DISTANCE MATRICES
\begin{figure}
        \centering

@@

% RESULTS
\begin{figure}
        \centering

        %%% BRIGHT PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_bright.eps}    
        \caption{Bright}
        \label{subfig:pr_bright}
        \end{subfigure}
        ~ 
        %%% DIM PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dim.eps}    
        \caption{Dim}
        \label{subfig:pr_dim}
        \end{subfigure}
        ~
        %%% DARK PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dark.eps}    
        \caption{Dark}
        \label{subfig:pr_dark}
        \end{subfigure}
        ~ 
        %%% ALL PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_all.eps}    
        \caption{Comparison between datasets when both grayscale and depth images are utilized.}
        \label{subfig:pr_all}
        \end{subfigure}

        \hspace{-3mm}
        \caption{Precision vs. Recall curves of the results.}
        \label{fig:pr_curves}
\end{figure}

%----------------------------------------------------------------------------------------------------
% CONCLUSION
%----------------------------------------------------------------------------------------------------

\section{CONCLUSION}

In conclusion, this paper presents a novel image description technique that is used to achieve loop closure detection within a SLAM framework. The technique works quite rapidly and operates in real-time. Moreover, it results successful loop closing on different lightning conditions by using the depth information.
